### 2019-03-26 _publications/jors/paper.tex
Fix for @tonkmr review
First unfinished draft of intro rewrite focusing on the website rather
than phase field.

Scientific communities struggle with the challenge of effectively and
efficiently sharing content and data. An online portal provides a
valuable space for scientific communities to discuss challenges and
collate scientific results. Examples of such portals include the
Micromagenetic Modeling Group ($\mu$MAG~\cite{mumag}), the Iteratomic
Potentials Repository (IPR~\cite{}) and on a larger scale the NIH
Genetic Sequence Database (GenBank~\cite{}). In this work, we present
a description of a generic web portal that leverages existing online
services to provide a framework that may be adopted by other
scientific communities. The first deployment of the PFHub framework
supports phase-field practitioners and code developers participating
in an effort to improve quality assurance for phase-field codes.

@@

\section*{Introduction}

>>>>

Scientific communities struggle with the challenge of effectively and
efficiently sharing content and data. An online portal provides a
valuable space for scientific communities to discuss challenges and
collate scientific results. Examples of such portals include the
Micromagenetic Modeling Group ($\mu$MAG~\cite{mumag}), the Iteratomic
Potentials Repository (IPR~\cite{ipr1, ipr2}) and on a larger scale
the NIH Genetic Sequence Database (GenBank~\cite{genbank}). In this
work, we present a description of a generic web portal that leverages
existing online services to provide a framework that may be adopted by
other scientific communities. The first deployment of the PFHub
framework supports phase-field practitioners and code developers
participating in an effort to improve quality assurance for
phase-field codes.

@@

\section*{Introduction (new)}

Small scientific communities do not often have the resources to build
and host dedicated web infrastructure to support their varied content
and data requirements. In particular, hosting and supporting a complex
content management system (CMS) including web servers, web frameworks
and databases requires a great deal of configuration and long term
support and funding. Furthermore, a turnkey CMS solution may not meet
requirements for a particular scientific group that may require arcane
data formats, unusual data display and custom client-side automation.
The PFHub effort, instead of focusing on the CMS tool, focuses on
customizing and delivering the "client-side" requirements whilst
delegating back-end functionality to external services and then
integrate with those services' APIs. The PFHub current effort supports
a community of phase field code developers.

\section*{Introduction (old)}
